\LARGE \bf Planning with Attitude

### 2020-10-14 paper/main.tex
Final changes to the flexible sat section.

    \subsection{Satellite Attitude Keep-Out}
        % \todo{Let's add a little more detail here: How about saying the dynamics are \eqref{eq:rigid_body_dynamics} plus a few extra states to capture the bending modes. Also, let's just call the start tracker a camera or sensor.}
        A spacecraft with flexible appendages was tasked to perform a 150 degree slew maneuver while
        ensuring that a body-mounted camera did not point within 40 degrees ``keep-out zone'' around the sun vector. The spacecraft dynamics are presented in detail in~\cite{Tracy2020}, and are based
        on equation \eqref{eq:rigid_body_dynamics} with the addition of six states to account for three flexible modes. Control torques are generated by four reaction wheels.

        \todo{Kevin: add some info on cost function, initial guess (if any), etc.}

        We enforce the camera keep-out zone can with the following constraint,
        \begin{equation}
            \left(\inframe{W}{r_{sun}}\right)^T 
            \left(\toframe{W}{B}{A(q)} \, \inframe{B}{r_{cam}} \right) \leq \cos(40 ^\circ) ,
        \end{equation}
        where $^Br_{cam}$ is the camera line-of-sight unit vector in the body frame and $^Wr_{sun}$ is the unit vector pointing to the sun in the world frame. The attitudes that satisfy this constraint comprise a non-convex set, with the
        constraint itself being nonlinear in $q$.
        \begin{figure}[ht]
            \centering
            \includegraphics{figures/kevins_plots/attitude_slew_plot.tikz}
            \caption{Visualization of the flexible spacecraft slew with a keep-out zone. Attitude is parameterized with a Rodrigues parameter to visualize the trajectory in three dimensions. The constraint surface represents attitudes where the camera line-of-sight is within 40$^\circ$ of the sun. The unconstrained solution violates this constraint, while the constrained solution is able to avoid the keep out zone.}
            \label{fig:keepout}
        \end{figure}
        % \todo{Talk a little about the results in the plot here.}

        \todo{Kevin: looks like both versions of ALTRO worked fine on this problem, so we should probably not say all this group stuff. Maybe just comment on the timing results and try to offer an explanation.}

        ALTRO is able to reason about this nonlinear constraint, and account for the group
        structure present in the quaternion. From Figure \ref{fig:keepout} we can see that
        without the camera constraint present, the trajectory will pass through the keep-out
        zone, making the trajectory infeasible. With the keep-out zone constraint present, ALTRO
        is able to converge on a trajectory that performs the slew in an efficient manner, while
        keeping the camera sufficiently far from the sun.

>>>>

    \subsection{Satellite Attitude Keep-Out}
        % \todo{Let's add a little more detail here: How about saying the dynamics are \eqref{eq:rigid_body_dynamics} plus a few extra states to capture the bending modes. Also, let's just call the start tracker a camera or sensor.}
        A spacecraft with flexible appendages was tasked to perform a 150 degree slew maneuver while
        ensuring that a body-mounted camera did not point within 40 degrees of a  ``keep-out zone'' around the sun vector. The spacecraft dynamics are presented in detail in~\cite{Tracy2020}, and are based
        on equation \eqref{eq:rigid_body_dynamics} with the addition of six states to account for three flexible modes. Control torques are generated by four reaction wheels.  The slew is motivated by a quadratic cost function that penalizes error from the final attitude, as well as excessive flexible displacement. 
        % \todo{Kevin: add some info on cost function, initial guess (if any), etc.}
        We enforce the camera keep-out zone can with the following constraint,
        \begin{equation}
            \left(\inframe{W}{r_{sun}}\right)^T 
            \left(\toframe{W}{B}{A(q)} \, \inframe{B}{r_{cam}} \right) \leq \cos(40 ^\circ) ,
        \end{equation}
        where $^Br_{cam}$ is the camera line-of-sight unit vector in the body frame and $^Wr_{sun}$ is the unit vector pointing to the sun in the world frame. The attitudes that satisfy this constraint comprise a non-convex set, with the
        constraint itself being nonlinear in $q$.
        \begin{figure}[ht]
            \centering
            \includegraphics{figures/kevins_plots/attitude_slew_plot.tikz}
            \caption{Visualization of the flexible spacecraft slew with a keep-out zone. Attitude is parameterized with a Rodrigues parameter to visualize the trajectory in three dimensions. The constraint surface represents attitudes where the camera line-of-sight is within 40$^\circ$ of the sun. The unconstrained solution violates this constraint, while the constrained solution is able to avoid the keep out zone.}
            \label{fig:keepout}
        \end{figure}

        ALTRO is able to converge on a feasible trajectory for this problem without any initial guess, with the resulting attitude history represented in Fig. \ref{fig:keepout}. Without the camera constraint present, the trajectory will pass through the keep-out
        zone, making the trajectory infeasible. With the keep-out zone constraint present, ALTRO
        is able to generate a trajctory that performs the slew in an efficient manner, while
        keeping the camera sufficiently far from the sun.
